Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex
Cambios intro

\Cref{fig:car,fig:plane} show the schematics of a car frame and a fuselage section, both enclosing crash boxes. For these applications, adhesives are very competitive both in bonding strength and in economical manufacturing costs (Jones, \cite{superyacht}). In order to check adhesive's suitability for their use in crashworthy elements, this research develops numerical models of adhesively bonded crash boxes subjected to impact loads using finite element models. Information and data present in the literature are used to create and validate these models in order to ensure the accuracy of the results.

>>>>

\Cref{fig:car,fig:plane} show the schematics of a car frame and a fuselage section, both enclosing crash boxes. In this research, a finite element model of an adhesive-bonded energy absorber subjected to impact loads is studied. The specimen is defined and optimized according to crashworthiness metrics in order to better its performance as a crashworthy element. Information and data present in the literature are used to create and validate these models in order to ensure the accuracy of the results.
